Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-23 manuscript/supplemental_material.Rnw
include too many alignment in star plot

\begin{table}
  \begin{tabular}{c c c c}
    \toprule
    Species                       & Common Name        & Reference & Read Length \\
    \midrule
    \textit{Ateles fusciceps}     & Spider monkey      & \textit{Homo sapiens} & 100 \\
    \textit{Bos taurus}           & Cow                & UMD3.1     & 75 \\
    \textit{Canis familiaris}     & Dog                & CanFam3.1  & 150 \\
    \textit{Dasypus novemcinctus} & 9-Banded Armadillo & DASNOV3    & 100 \\
    \textit{Equus caballus}       & Horse              & EquCab2    & 100 \\ 
    \textit{Loxodonta africana}   & Elephant           & loxAfr3    & 75 \\
    \textit{Homo sapiens}         & Human              & GRCh38     & 75, 150 \\
    \textit{Monodelphis domestica} & Opossum           & BROAD05    & 75 \\
    \textit{Mus musculus}         & Mouse              & GRCm38     & 35,44,150 \\
    \textit{Ovis aries}           & Sheep              & Oar\_v3.1   & 151 \\
    \textit{Pan paniscus}         & Bonobo             & CHIMP2.1.4 & 150 \\
    \textit{Spalax carmeli}       & Blind mole rat     & \textit{Mus musculus} & 100 \\
    \textit{Spalax galili}   & Blind mole rat     & \textit{Mus musculus} & 100 \\
    \textit{Sus scrofa}           & Duroc (pig)        & Sscrofa10.2 & 51 \\
    \bottomrule
  \end{tabular}
  \caption{Species names, common names, reference genomes and read 
    lengths for aligned species. An italic species as a reference 
    indicates that assembled reads were annotated using the corresponding
    reference genome as explained in the text.}
  \label{tab:ref_genome_aligned_species}
\end{table}

@@

\begin{figure}[hb]
<<transcriptome.mapping.figure,fig.width=8,fig.height=8,echo=FALSE>>=
star.logs.unmapped <- 
    star.logs[grepl("%",field) & 
                  grepl("unmapped",field) & 
                      !grepl("too many mismatches",field),]
star.logs.unmapped <- 
    star.logs.unmapped[,field:=capfirst(gsub("\\% of reads unmapped: ","",field))]
pushViewport(viewport(layout=grid.layout(ncol=1,nrow=2,heights=c(2,1))))
print(ggplot(star.logs.unmapped,
             aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
      + geom_boxplot()
      + facet_grid(field~.,scales="free")
      + ylab("Percent of Reads")
      + xlab(NULL)
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,0,0,1.1),"strwidth",data=list("","","","e8")),
              axis.title.x=element_blank(),
              axis.text.x = element_blank()),#element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=1)
      )
pushViewport(viewport(layout.pos.col=1,layout.pos.row=1))
grid.text("A",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport()          
print(ggplot(star.logs[grepl("input reads$",field),],
             aes(x=capfirst(species),y=as.numeric(value)))
      + geom_boxplot()
      + scale_y_log10()
      + ylab("Reads")
      + xlab("Species")
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,1.6,0,0),"strheight",data=list("","TO","","")),
              axis.text.x = element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=2))
pushViewport(viewport(layout.pos.col=1,layout.pos.row=2))
grid.text("B",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport(2)
@ 
\caption{RNAseq read and alignment statistics for all species. A)
  Boxplot of percentages of unmapped reads in each species; 0\% of
  reads in all species were unmapped because of mismatches. B) Boxplot
  of number of RNAseq reads in each species.}
\label{fig:transcriptome_statistics}
\end{figure}

>>>>

\begin{table}[hb]
  \centering
  \begin{tabular}{c c c c}
    \toprule
    Species                       & Common Name        & Reference & Read Length \\
    \midrule
    \textit{Ateles fusciceps}     & Spider monkey      & \textit{Homo sapiens} & 100 \\
    \textit{Bos taurus}           & Cow                & UMD3.1     & 75 \\
    \textit{Canis familiaris}     & Dog                & CanFam3.1  & 150 \\
    \textit{Dasypus novemcinctus} & 9-Banded Armadillo & DASNOV3    & 100 \\
    \textit{Equus caballus}       & Horse              & EquCab2    & 100 \\ 
    \textit{Loxodonta africana}   & Elephant           & loxAfr3    & 75 \\
    \textit{Homo sapiens}         & Human              & GRCh38     & 75, 150 \\
    \textit{Monodelphis domestica} & Opossum           & BROAD05    & 75 \\
    \textit{Mus musculus}         & Mouse              & GRCm38     & 35,44,150 \\
    \textit{Ovis aries}           & Sheep              & Oar\_v3.1   & 151 \\
    \textit{Pan paniscus}         & Bonobo             & CHIMP2.1.4 & 150 \\
    \textit{Spalax carmeli}       & Blind mole rat     & \textit{Mus musculus} & 100 \\
    \textit{Spalax galili}   & Blind mole rat     & \textit{Mus musculus} & 100 \\
    \textit{Sus scrofa}           & Duroc (pig)        & Sscrofa10.2 & 51 \\
    \bottomrule
  \end{tabular}
  \caption{Species names, common names, reference genomes and read 
    lengths for aligned species. An italic species as a reference 
    indicates that assembled reads were annotated using the corresponding
    reference genome as explained in the text.}
  \label{tab:ref_genome_aligned_species}
\end{table}

@@

\begin{figure}[hb]
<<transcriptome.mapping.figure,fig.width=8,fig.height=8,echo=FALSE>>=
star.logs.unmapped <- 
    star.logs[grepl("%",field) & 
                  grepl("unmapped|too many loci",field) & 
                      !grepl("too many mismatches",field),]
star.logs.unmapped <- 
    star.logs.unmapped[,field:=capfirst(gsub("\\% of reads (unmapped:|mapped to) ","",field))]
pushViewport(viewport(layout=grid.layout(ncol=1,nrow=2,heights=c(2,1))))
print(ggplot(star.logs.unmapped,
             aes(x=capfirst(species),y=as.numeric(gsub("%","",value))))
      + geom_boxplot()
      + facet_grid(field~.,scales="free")
      + ylab("Percentage of Reads Unmapped")
      + xlab(NULL)
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,0,0,1.1),"strwidth",data=list("","","","e8")),
              axis.title.x=element_blank(),
              axis.text.x = element_blank()),#element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=1)
      )
pushViewport(viewport(layout.pos.col=1,layout.pos.row=1))
grid.text("A",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport()          
print(ggplot(star.logs[grepl("input reads$",field),],
             aes(x=capfirst(species),y=as.numeric(value)))
      + geom_boxplot()
      + scale_y_log10()
      + ylab("Reads")
      + xlab("Species")
      + theme_bw()
      + theme(legend.position="top",
              plot.margin=unit(c(0,1.6,0,0),"strheight",data=list("","TO","","")),
              axis.text.x = element_text(angle = 30, hjust = 1, vjust=1,face="italic")),
      vp=viewport(layout.pos.col=1,layout.pos.row=2))
pushViewport(viewport(layout.pos.col=1,layout.pos.row=2))
grid.text("B",
          y=unit(1,"npc")-unit(0.1,"cm"),
          x=unit(0,"npc")+unit(0.1,"cm"),
          gp=gpar(fontsize=24),
          just=c("left","top"))
popViewport(2)
@ 
\caption{RNAseq read and alignment statistics for all species. A)
  Boxplot of percentages of unmapped reads in each species; 0\% of
  reads in all species were unmapped because of mismatches. B) Boxplot
  of number of RNAseq reads in each species.}
\label{fig:transcriptome_statistics}
\end{figure}
